A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Simplify the use of MAM

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace \cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adapt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

Using MAM as a data storage benefits from the scalability of the underlying IOTA network as well as the decentralized and fault-tolerant characteristics of distributed ledgers, which reduce the risks of centralized storage services. Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

@@

\subsubsection{A Traceable Data Stream}
Data traceability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

>>>>

Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, which introduces properties like publishing, classifying and tracking authenticated message streams. It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

Using MAM as a data storage benefits from the underlying IOTA network as well as the decentralized and fault-tolerant characteristics, which reduce the risks of centralized storage services. Furthermore, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

@@

\subsubsection{A Traceable Data Stream}
It allows users to track the changes of data. The hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it is not straightforward to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
